\begin{abstract}

Molten salts have been used for nuclear applications since the first half of the 20th century. Recent interests garnered into Molten Salt Reactors and Concentrated Solar Power applications has resulted in renewed focus on Molten salt, justified by their properties. However, experimental data on important thermo-physical properties is sparse and scattered over 4 decades of publications. This creates difficulty in advancing the research related to applications of Molten Salts. The aim of this project was to initiate development of an open source molten salt database library. Experimental data of multiple salts is gathered via Literature sweep and matrix search. Obtained data is converted to a newly developed Advanced Scientific Data Format (ASDF) and published on \url{https://github.com/openmsr/msdl}. Two computational tools were developed to supplement the project, a Parser that can easily convert raw experimental data into the desired data structure to make external contribution easier. Also developed was an Application Programming Interface (API) to aid with extracting, filtering and data filtering for salt mixtures of interest. By the end of the timeline of this project 133 data sets containing values of 7 different properties were obtained, converted to ASDF and added to the data library.


    
\end{abstract}

% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf

\newpage
